The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
edit fig captions

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts.

@@

(ref:socres) Varying scale in social threshold. For each social threshold (5 m,
50 m, 100 m, 150 m, 200 m, 250 m, 300 m, 350 m, 400 m, 450 m, 500 m), multilayer
networks were constructed for each landcover class (forest, lichen and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g.: open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution (10 m, 100 m, 250 m, 500 m and 1000 m), multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter), and four network metrics were calculated and we
examined how network metrics changed as a function of changes in spatial scale.
A) Mean graph strength of individuals was weaker during the summer compared to
the winter months. B) Mean layer relevance showed sparse connectivity in summer
compared to winter networks and a decrease in winter lichen layer relevance at
higher landcover resolutions. C) Similarity of landcover network layers between
seasons (e.g.: open summer compared to open winter) showed different responses
to changing landcover scale with an increase in similarity for forest layers at
250 m and decrease in similarity for open layers at 250 m. Note that lichen
layer similarity is not shown because individuals did not interact in lichen
habitats greater greater than 10 m landcover resolution. D) Mean connective
redundancy across individuals showed a decreasing trend with increasing
landcover resolution.

>>>>

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts (Figure 2).

@@

(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, lichen and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g.: open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter), and four network metrics were calculated and we
examined how network metrics changed as a function of changes in spatial scale.
A) Mean graph strength of individuals was weaker during the summer compared to
the winter months. B) Mean layer relevance showed sparse connectivity in summer
compared to winter networks and a decrease in winter lichen layer relevance at
higher landcover resolutions. C) Similarity of landcover network layers between
seasons (e.g.: open summer compared to open winter) showed different responses
to changing landcover scale with an increase in similarity for forest layers at
250 m and decrease in similarity for open layers at 250 m. Note that lichen
layer similarity is not shown because individuals did not interact in lichen
habitats greater greater than 10 m landcover resolution. D) Mean connective
redundancy across individuals showed a decreasing trend with increasing
landcover resolution.
